---
title: "graphs"
author: "vishnusagar2021"
date: "2/7/2021"
output: html_document
---
# R base
##pie chart in 
pie(x,labels, radius, main, col, clockwise)

x= vector
lables = discription to the vectors
radius = -1 to +1
main = title of chart
col= color for chart
colockwise = clockwise and anticlockwise  T/F


```{r}
#eg
x= c(20,15,25,30,10)

labels= c("sugu","rosy","sixer","corona","covid")

#eg1

pie(x,labels, radius = 1,main = "hostel",col=rainbow (5), colockwise = F)
#eg2

pie(x,labels, radius = 1,main = "hostel",col=c("purple", "violetred1", "green3",
"cornsilk", "cyan", "white"), colockwise = F)

#eg3




```

##saving a graph/diagram
1) x= c(20,15,25,30,10)..............................data for graph

labels= c("sugu","rosy","sixer","corona","covid")

2) png(file="filename.png")................chart file name

3) pie(x,labels, radius = 1,main = "hostel",col=rainbow (5), colockwise = F)

4) dev.off() ..............for svaing the file
``


```{r}
x= c(20,15,25,30,10)
labels= c("sugu","rosy","sixer","corona","covid")
png(file= "hostel.png")
pie (x,labels, radius = 1,main = "hostel", col=rainbow (5))

dev.off()
```
#percentage pie
```{r}
piepercent=round(100*x/sum(x),1)
pie(x,labels=piepercent, radius = 1,main = "hostel", col=rainbow(length(x)))
legend("topright", c("sugu","rosy","sixer","corona","covid"), cex=0.5, fill=rainbow(length(x)))

```
##3D pie chart
library("plotrix")
```{r}
install.packages("plotrix")
library("plotrix")
pie3D(x,labels=labels, explode=0.1, main = "hostel")



```
#Bar diagaram
barplot(H,xlab,ylab,main,names.arg, col)
H-data
xlab- x axis label
ylab- y axis label
main - chart title
names.arg- vecor containing names for each bar
col- color for bar
```{r}
png(file="bar.png")
H=c(8,12,9,11,6)
label= c("S1","S2","S3","S4","S5")
barplot(H, xlab = "stations",ylab = "TDS(mg/L)", names.arg = label,col= "blue", border = "black")
dev.off()

```
```{r}
H=c(8,12,9,11,6)
label= c("S1","S2","S3","S4","S5")
barplot(H, xlab = "stations",ylab = "TDS(mg/L)", main= "WQ data", names.arg = label,col= "blue", border = "black")
```
#group bar chart and stacked barchart

```{r}
colors= c("blue","green", "red")
Station= c("S1","S2","S3","S4","S5")
quality= c("good","bad", "poor")

values=matrix(c(20:34),nrow=3, ncol=5, byrow=T)
values

barplot(values,xlab = "Stations", ylab="EU", main="quality data", names.arg = Station, col=colors, border= "black")
legend("topright",quality, cex= 0.7, fill=colors)
```

```{r}
colors= c("blue","green", "red")
Station= c("S1","S2","S3","S4","S5")
quality= c("good","bad", "poor")

values=matrix(c(20:34),nrow=3, ncol=5, byrow=T)
values
png(file="group_bar.png")
barplot(values,xlab = "Stations", ylab="EU", main="quality data", names.arg = Station, col=colors, border= "black")
legend("topright",quality, cex= 0.7, fill=colors)
dev.off()
```

